MsCcHSFeed Outline

### 2022-02-25 MsCcHSFeedOutlineDec15.Rmd
Fixed means for eclosion to not run into plyr/dplyr error and get SEs

```{r}
library(ggplot2)
library(tidyverse)
#library(Rmisc)
library(lubridate)
library(lmerTest)
```

@@

@@

```{r}
eclosmeans <- datawasp %>%
  group_by(food, treatment) %>%
    summarise(mean = mean(percent))

>>>>

```{r}
library(ggplot2)
library(tidyverse)
library(Rmisc)
library(lubridate)
library(lmerTest)
```

@@

```{r}
eclosmeans <- summarySE(datawasp, measurevar = "percent", groupvars = c("food", "treatment"))

@@
